\documentclass{JINST}
%\documentclass{article}

\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amssymb,amsmath}
\usepackage{delarray}

%\usepackage[cp1251]{inputenc}       % declare this file encoding
%\usepackage[english,russian]{babel} % declare Russian to be default but keep English available

\title{LYSO:Ce and LuYAG:Pr light yield and energy resolution comparison}

\author{E.A.Babichev\ $^a$, S.E.Baru\ $^a$, D.N.Grigoriev\ $^a$, V.P.Oleynikov\ $^{a,b}$, V.V.Porosev\ $^a$\thanks{Corresponding author.}, G.A.Savinov\ $^a$, Stephane Callier\ $^c$
\\
\llap{$^a$}Budker Institute of Nuclear Physics, \\Lavrentiev ave. 11, Novosibirsk 630090, RUSSIA, \\
\llap{$^b$}Novosibirsk State University,\\ Pirogova st. 2, Novosibirsk 630090, RUSSIA,\\
\llap{$^c$}OMEGA Ecole Polytechnique-CNRS/IN2P3, Palaiseau, France\\


E-mail: \email{porosev@inp.nsk.su}}


\abstract{bla-bla-bla}

\keywords{LYSO:Ce, LuYAG:Pr, Scintillator light yield, Energy resolution of PMT detector, Light collection Monte Carlo simulation }

\begin{document}


\section{Introduction}
\hspace*{\parindent}

Неорганические сцинтилляторы играют важную роль в детектировании фотонов. Сцинтилляторы имеют широкое практическое применение в физике высокий энергий и медицинских рентгеновских приборах.
Основные требования, предъявляемые к сцинтиллятору - это высокое энергетическое разрешение, малое время высвечивания и высокая останавливающая способность. На данный момент существует огромное количество различных видов сцинтиллятов, свойства которых варьируются в широких пределах \cite{Ref_SCINTLBL}.

\section{Energy resolution of the detector}
\hspace*{\parindent}


\section{Experiment}
\hspace*{\parindent}

\section{Monte Carlo simulation}
\hspace*{\parindent}


\section{Results and discussion}
\hspace*{\parindent}


\section{Energy resolution of the detector}
\hspace*{\parindent}



\section{Conclusion}
\hspace*{\parindent}





\section{Acknowledgements}


\newpage
\begin{thebibliography}{99}

\bibitem{Ref_SCINTLBL}
http://scintillator.lbl.gov/








\bibitem{Ref_MWPC}
S.E.Baru, A.G.Khabakhpashev, I.R.Makarov, G.A.Savinov, L.I.Shekhtman, V.A.Sidorov, \emph{Digital X-ray imaging installation for medical diagnostics.} Nucl.Instr.and Meth. A238 (1985), p.165

\bibitem{Ref_MIC1}
E.A.Babichev, S.E.Baru, V.R.Groshev, A.G.Khabakhpashev, V.V.Porosev, G.A.Savinov, L.I.Shekhtman,V.I.Telnov, \emph{Photon counting and integrating analog gaseous detectors for digital scanning radiography.} Nuclear Instruments and Methods in Physics Research, A419(1998) p.290-294

\bibitem{Ref_MIC2}
E.A.Babichev, S.E.Baru, V.R.Groshev, A.G.Khabakhpashev,G.S.Krainov, V.V.Leonov,V.A.Neustroev, V.V.Porosev, G.A.Savinov, L.I.Shekhtman
\emph{Usage of two types of high pressure Xenon chambers for medical radiography.} Nuclear Instruments and Methods in Physics Research, A461 (2001) p.430-434

\bibitem{Ref_MIC3}
E. A. Babichev, S. E. Baru, D. N. Grigoriev, V. R. Groshev, V. V. Leonov, P. A. Papushev, V. V. Porosev, G. A. Savinov, V. R. Shayakhmetov, L. I. Shekhtman, Yu. A. Tikhonov, Yu. G. Ukraintsev, \emph{High-resolution detectors for medical applications and synchrotron radiation research.} Nuclear Instruments and Methods in Physics Research, A628 (2011), Issue 1, p.440-443.

\bibitem{Ref_SiPMPULSE}
Stefan Seifert, Herman T. van Dam, Jan Huizenga, Ruud Vinke, Peter Dendooven, Herbert LГ¶hner, Dennis R. Schaart, \emph{Simulation of silicon photomultiplier signals.} IEEE TRANSACTIONS ON NUCLEAR SCIENCE, VOL. 56, NO. 6, December 2009, p.3726-3733

\bibitem{Ref_SiPMSHAPE}
Virginia Ch. Spanoudaki and Craig S. Levin. \emph{Scintillation induced response in passively-quenched Si-based single photon counting avalanche diode arrays.} Opt Express. 2011 Jan 17; 19(2):1665-79.

\bibitem{Ref_MPPCQE}
K. Yamamoto, K. Yamamura, K. Sato, S. Kamakura, T. Ota, H. Suzuki, S. Ohsuka, \emph{Development of Multi-Pixel Photon Counter (MPPC).} 2007 IEEE Nuclear Science Symposium Conference Record N24-292

\bibitem{Ref_MELMOUNT}
Th.Kirn, M.Haring, D. Schmitz, W. Schulz, \emph{Absorption length, radiation hardness and aging of different optical glues.} CMS NOTE 1999 003.

\bibitem{Ref_ADC200ME}
P. A. Bak, A. M. Batrakov, R. A. Kadyrov, P. V. Logachev, A. V. Pavlenko, A. N. Panov, V. Ya. Sazanskii, G. A. Fatkin, \emph{Control system of a linear induction accelerator of an X-ray complex: Structure, hardware, and test performance.} Optoelectronics, Instrumentation and Data Processing. June 2011, Volume 47, Issue 3, pp 303-312

\bibitem{Ref_EASIROC}
Stephane Callier, Christophe Dela Taille, Gisele Martin-Chassard, Ludovic Raux, \emph{EASIROC, an easy and versatile ReadOut device for SiPM.} Physics Procedia 37 ( 2012 ) p.1569-1576

\bibitem{Ref_LURES}
M. Balcerzyk, M. Moszynski, M. Kapusta, D. Wolski, \emph{YSO, LSO, GSO and LGSO. A Study of Energy Resolution and Nonproportionality.} IEEE Transactions on Nuclear Science (2000), Volume 47, Issue 4, p.1319 - 1323

\bibitem{Ref_LURES2}
A. Phunpueok, W. Chewpraditkul, P. Limsuwan, C. Wanarak, \emph{Light output and energy resolution of $Lu_{0.7}Y_{0.3}AlO_{3}:Ce$ and
$Lu_{1.95}Y_{0.05}SiO_{5}:Ce$ scintillators.} Procedia Engineering 32 (2012) p.564-570



\end{thebibliography}



\end{document}
